sensi_an_rotations1. Start of sensitivity analysis for rotations.

### 2018-12-06 inst/documents/rotations_notes.Rmd
tweaks

>>>>

fix :
Warning: Error in raf_get: object 'RAF' not found
run_rot() can create it but when I add breakpoints it disappears

where is raf_get called ?
insecticide_check()
rot_migrate()

I suspect problem is here in insecticide_check()    
#end of rotation reached
    if (gens_this_insecticide >= rot_interval) 
      {
      # 31/7/18 I could add a check in here for case
      # where only this insecticide remains below resistance threshold
      # in which case don't want to change
      # if I reset gens-this-insecticide then it will be used for another rot_interval
      #I can use either of these to get the freqs for all other insecticides
      # RAF[-current_insecticide, 'f','intervention',1]

e.g.
raf_get(a)
Error in raf_get(a) : object 'a' not found
